Using Bayesian Regression to Quantify Sexual Dimorphism in Dinosaurs

### 2024-02-15 paperAndPoster/paper.tex
fix: minor edits to pdf and docx of paper

\title{Using Bayesian Regression to Quantify Sexual Dimorphism in Dinosaurs}
\author{Eric Campbell}
\begin{document}
\maketitle

@@

\begin{align*}
\text{Length}_{ m / f } &\sim \mathcal{N}\left(\mu_{ m / f }, \sigma\right) \\
\mu_m &= 3.79 * \left(1 - 0.94e^{-0.0695 \ast \text{age}}\right) \\
\mu_f &= 2.78 * \left(1 - 0.91e^{-0.0926 \ast \text{age}}\right) \\
\sigma &= 0.25
\end{align*}

@@

\begin{align*}
\text{Length}_{m/f,i} &\sim \normal{\mu_{m/f, i}}{\sigma} \\
\mu_{m/f, i} &= \text{von Betlananffy}(\text{age}_i, L_{ m/f }, A_{ m/f }, K_{ m/f }) \\
L_{ m/f } &\sim \normal{\text{population L}}{0.5} \\
A_{ m/f } &\sim \normal{\text{population A}}{0.025} \\
K_{ m/f } &\sim \normal{\text{population K}}{0.05} \\
\sigma &\sim \normal{0.25}{0.05} \\
\end{align*}

@@

As shown above, the modification of the method in \cite{saittaEffectSizeStatistical2020} using Bayesian regression to calculate the posterior distributions for sex-specific growth curves and the level of sexual dimorphism is generally reliable and useful way to quantify dimorphism in extinct populations. While it shares some weakness with with the original method, it also has several notable advantages. One is that by carrying uncertainty through all parts of modelling, the final result contains more information about the process \parencite{mcelreathStatisticalRethinkingBayesian2020}. Another is that by incorporating prior knowledge, we can constrain our final result to be biologically plausible.

>>>>

\title{Using Bayesian Regression to Quantify Sexual Dimorphism in Dinosaurs}
\author{Eric Campbell \\ \texttt{eric.robert.campbell@gmail.com}}
\date{}
\begin{document}
\maketitle

@@

\begin{align*}
\text{Length}_{ m / f } &\sim \mathcal{N}\left(\mu_{ m / f }, \sigma_{m/f}\right) \\
\mu_m &= 3.79 * \left(1 - 0.94e^{-0.0695 \ast \text{age}}\right) \\
\mu_f &= 2.78 * \left(1 - 0.91e^{-0.0926 \ast \text{age}}\right) \\
\sigma_{m/f} &= 0.25
\end{align*}

@@

\begin{align*}
\text{Length}_{m/f,i} &\sim \normal{\mu_{m/f, i}}{\sigma} \\
\mu_{m/f, i} &= \text{von Betlananffy}(\text{age}_i, L_{ m/f }, A_{ m/f }, K_{ m/f }) \\
L_{ m/f } &\sim \normal{\text{population L}}{0.5} \\
A_{ m/f } &\sim \normal{\text{population A}}{0.025} \\
K_{ m/f } &\sim \normal{\text{population K}}{0.05} \\
\sigma_{m/f} &\sim \normal{0.25}{0.05} \\
\end{align*}

@@

As shown above, the modification of the method in \cite{saittaEffectSizeStatistical2020} using Bayesian regression to calculate the posterior distributions for sex-specific growth curves and the level of sexual dimorphism is a generally reliable and useful way to quantify dimorphism in extinct populations. While it shares some weakness with the original method, it also has several notable advantages. One is that by carrying uncertainty through all parts of modelling, the final result contains more information about the process \parencite{mcelreathStatisticalRethinkingBayesian2020}. Another is that by incorporating prior knowledge, we can constrain our final result to be biologically plausible.
